How predictable is extinction?

### 2018-10-11 doc/gsa2018_talk.tex
some name reshuffles. growing talk.

  \begin{center}
    \begin{LARGE}
      Extinction is \alert{hard} to predict, \\but is extremely \alert{important} to conservation decisions.
    \end{LARGE}
  \end{center}

@@

\begin{frame}
  \frametitle{In-sample predictive performance}
  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{../results/figure/roc_hist}

@@

  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{../results/figure/fold_ts}

>>>>

  \begin{center}
    \begin{LARGE}
      Extinction is \alert{hard} to predict, but is \alert{important} to conservation decisions.
    \end{LARGE}
  \end{center}

@@

\begin{frame}
  \frametitle{In-sample predictive performance, full dataset}

  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{../results/figure/roc_hist}

\begin{frame}
  \frametitle{In-sample predictive performance, by time}

  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{../results/figure/roc_ts}

@@

  \includegraphics[width=\textwidth,height=\textheight,keepaspectratio=true]{../results/figure/fold_auc_time}
